\vspace{-2.0cm} \textbf{Talking with signs} \\ \Large \textbf{A self supervised method to detect nouns and numbers in a non-annotated signs language corpus}

### 2023-06-18 articles/2021/self-supervised-method-to-detect-nouns-and-numbers/article-tesis.tex

% nSDmV2 5% of the dataset
\begin{table*}
\captionsetup{font=footnotesize}
\centering
\begin{tabular}{ p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} }
\toprule
\multicolumn{5}{c}{\textbf{nSDmV2 Training Results with the 5\% of the dataset}} \\
\hline
\hline
\textbf{Epoch}&	\textbf{Loss}	&\textbf{Precision}	&\textbf{Recall}	&\textbf{AUC} \\
\hline
\midrule
Epoch 1&	2.7568&	0.0000e+00&	0.0000e+00&	0.0911\\
Epoch 2&	2.6647&	0.0000e+00&	0.0000e+00&	0.1008\\
Epoch 3&	2.6455&	0.0000e+00&	0.0000e+00&	0.1017\\
Epoch 4&	2.6296&	0.0000e+00&	0.0000e+00&	0.1193\\
Epoch 5&	2.6121&	0.0000e+00&	0.0000e+00&	0.1222\\
Epoch 6&	2.6032&	0.0000e+00&	0.0000e+00&	0.1222\\
Epoch 7&	2.5943&	0.0000e+00&	0.0000e+00&	0.1229\\
Epoch 8&	2.5875&	0.0000e+00&	0.0000e+00&	0.1229\\
Epoch 9&	2.5825&	0.0000e+00&	0.0000e+00&	0.1229\\
Epoch 10&	2.5790&	0.0000e+00&	0.0000e+00&	0.1229\\
\bottomrule
\end{tabular}
\caption{Shows results of training the nSDmV2 model with the 5\% of the labeled PSL dataset: (1)\textit{Epoch} identifies the epoch in in the training process (2)\textit{Loss} obtained loss (3)\textit{Precision} obtained precision (4)\textit{Recall} obtained recall (5)\textit{AUC} area under the precision-recall curve.}
\label{tab:nSDmV2-detection-results-5-percent}
\end{table*}

% nSDmV3 5% of the dataset
\begin{table*}
\captionsetup{font=footnotesize}
\centering
\begin{tabular}{ p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} }
\toprule
\multicolumn{5}{c}{\textbf{nSDmV3 Test Results with the 5\% of the dataset}} \\
\hline
\hline
\textbf{Epoch}&	\textbf{Loss}	&\textbf{Precision}	&\textbf{Recall}	&\textbf{AUC} \\
\hline
\midrule
Epoch 1&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 2&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 3&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 4&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 5&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 6&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 7&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 8&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 9&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 10&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
\bottomrule
\end{tabular}
\caption{Shows results of testing the nSDmV3 model with the 5\% of the labeled PSL dataset: (1)\textit{Epoch} identifies the epoch in in the training process (2)\textit{Loss} obtained loss (3)\textit{Precision} obtained precision (4)\textit{Recall} obtained recall (5)\textit{AUC} area under the precision-recall curve.}
\label{tab:nSDmV3-detection-results-5-percent}
\end{table*}

>>>>

% nSDmV2 5% of the dataset
\begin{table*}
\captionsetup{font=footnotesize}
\centering
\begin{tabular}{ p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} }
\toprule
\multicolumn{3}{c}{\textbf{nSDmV2 Training Results}} \\
\hline
\hline
\textbf{Epoch}&	\textbf{Loss}		&\textbf{AUC} \\
\hline
\midrule
Epoch 1&	2.7568&	0.0911\\
Epoch 2&	2.6647&	0.1008\\
Epoch 3&	2.6455&	0.1017\\
Epoch 4&	2.6296&	0.1193\\
Epoch 5&	2.6121&	0.1222\\
Epoch 6&	2.6032&	0.1222\\
Epoch 7&	2.5943&	0.1229\\
Epoch 8&	2.5875&	0.1229\\
Epoch 9&	2.5825&	0.1229\\
Epoch 10&	2.5790&	0.1229\\
\bottomrule
\end{tabular}
\caption{Shows results of training the nSDmV2 model with the labeled train PSL dataset: (1)\textit{Epoch} identifies the epoch in in the training process (2)\textit{Loss} obtained loss (3)\textit{Precision} obtained precision (4)\textit{Recall} obtained recall (5)\textit{AUC} area under the precision-recall curve.}
\label{tab:nSDmV2-detection-results-5-percent}
\end{table*}

% nSDmV3 5% of the dataset
\begin{table*}
\captionsetup{font=footnotesize}
\centering
\begin{tabular}{ p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} }
\toprule
\multicolumn{5}{c}{\textbf{nSDmV3 Train Results}} \\
\hline
\hline
\textbf{Epoch}&	\textbf{Loss}	&\textbf{Precision}	&\textbf{Recall}	&\textbf{AUC} \\
\hline
\midrule
Epoch 1&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 2&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 3&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 4&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 5&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 6&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 7&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 8&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 9&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
Epoch 10&	X.XXXX&	X.XXXX&	X.XXXX&	X.XXXX\\
\bottomrule
\end{tabular}
\caption{Shows results of testing the nSDmV3 model with the 5\% of the labeled PSL dataset: (1)\textit{Epoch} identifies the epoch in in the training process (2)\textit{Loss} obtained loss (3)\textit{Precision} obtained precision (4)\textit{Recall} obtained recall (5)\textit{AUC} area under the precision-recall curve.}
\label{tab:nSDmV3-detection-results-5-percent}
\end{table*}
